The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-08-02 paper/paper.Rmd
Added comp_x_var argument to create_focal_vs_comp()

```{r scbi-focal-vs-comp}
focal_vs_comp_scbi <- growth_scbi %>%
  create_focal_vs_comp(comp_dist, blocks = blocks_scbi, id = "stemID")
focal_vs_comp_scbi %>% 
  select(focal_ID, focal_sp, geometry, growth, comp)
```

>>>>

```{r scbi-focal-vs-comp}
focal_vs_comp_scbi <- growth_scbi %>%
  create_focal_vs_comp(comp_dist, blocks = blocks_scbi, id = "stemID", comp_x_var = "agb")
focal_vs_comp_scbi %>% 
  select(focal_ID, focal_sp, geometry, growth, comp)
```
